Social Computing Article\thanks{This title is temporary}

### 2013-01-14 Article.tex
Atualizei os headings (acho que tinha que ficar tudo em maísuculo)

\subsection{Copying and Guessing are beneficial to the Algorithm's Performance}

Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3). The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a peak in ({\em copy rate}: 7, {\em guess rate}: 0) and a valley in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions. Also, as shown in Figure 4, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

@@

\subsection{Evaluating the neighbours' solutions is beneficial}

>>>>

\subsection{Copying and Guessing are Beneficial to the Algorithm's Performance}

Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3). The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a maximum in ({\em copy rate}: 7, {\em guess rate}: 0) and a minimum in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions. Also, as shown in Figure 4, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

@@

\subsection{Evaluating the Neighbours' Solutions is Beneficial}
